### 2013-06-30 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding scaling figure  captions

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_pure_strong.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition.} \textit{Super-linear
      speed-up from memory thrashing in base case. MCLS is an order
      of magnitude slower arithmetically, causing the higher
      efficiency.}}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_weak_absolute.pdf}
  \end{center}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_weak_implementation.pdf}
  \end{center}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_strong_ms_eff.pdf}
  \end{center}
  \caption{\small{Absolute parallel efficiency relative to
      16-core 1-set base case.}}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_strong_ms_time.pdf}
  \end{center}
  \caption{\small{Wall time in seconds to solution for each
      case.}}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_weak_ms_eff.pdf}
  \end{center}
  \caption{Absolute parallel efficiency relative to 16-core
    1-set base case.}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{titan_weak_ms_time.pdf}
  \end{center}
  \caption{Wall time in seconds to solution for each case.}
\end{figure}

>>>>

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_pure_strong.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition absolute strong scaling.}
    \textit{Super-linear speed-up from memory thrashing in base
      case. MCLS is an order of magnitude slower arithmetically,
      causing the higher efficiency.}}
  \label{fig:titan_pure_strong}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_absolute.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition absolute weak scaling}}
  \label{fig:titan_weak_absolute}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_implementation.pdf}
  \end{center}
  \caption{\textbf{Pure domain decomposition implementation weak scaling}}
  \label{fig:titan_weak_implementation}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_eff.pdf}
  \end{center}
  \caption{\textbf{Absolute parallel efficiency relative to 16-core
      1-set base case.}}
  \label{fig:titan_strong_ms_eff}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case.}}
  \label{fig:titan_strong_ms_time}
\end{figure}

@@

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_ms_eff.pdf}
  \end{center}
  \caption{\textbf{Absolute parallel efficiency relative to 16-core
      1-set base case.}}
  \label{fig:titan_weak_ms_eff}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case.}}
  \label{fig:titan_weak_ms_time}
\end{figure}
